Is It Drift?

### 2021-08-26 graphs_newt_snakes/is_it_drift.Rmd
I updated my thoughts and concerces to is it drift R markdown. I also wrote about my next step plans

The phenotype vs food is a mess. I am having a lot of trouble seeing a potential trend. Maybe the way I chose to color the points is making this more difficult.

@@

Starting parameters:
sigma_i = 1, recomb=1e-8, sigma_in = 0.5, *sigma_M = 0.33*,  *K =1*,  SD = sigma_in,  SI = sigma_in,  surs = sigma_in,  SM = SI,  L = 4,  W = 35.0, G = 1e8, FECUN = 1/(L)),  RHO = FECUN/((1+FECUN) * K), initializeRecombinationRate(recomb)

Interaction Constants:
	 *interaction_rate = 0.05*,  PE = 0.1,  w = 10,  c = 0.0, *some_value = 30 (half number of new individuals)*,  *sc_size = 10 (selection coefficient)*

@@

@@

Yes <- c(8, 9, 11, 3, 16)/50
No <- c(42, 41, 39, 47, 34)/50

@@

Seems like having more individuals and a higher selection coefficient lead to the mutation spreading to all of the individuals in the population.

@@

Yes <- c(7, 10, 4, 0, 19)/50
No <- c(43, 40, 46, 50, 31)/50
snake_results_df <- data.frame(Notes, Yes, No)
knitr::kable(snake_results_df, "simple")
```

This is also the case when snakes get the mutation

@@

Snake_Yes <- 15/50
Newt_Yes <- 15/50
Snake_No <- 35/50
Newt_No <- 35/50

@@

When both species get the mutation I saw each combination happen sometimes the mutation would spread in both the snakes and newts populations. Other times only the mutation woyld only spread in one population and there were time when the mutation dies out in both populations.

>>>>

The phenotype vs food is a mess. I am having a lot of trouble seeing a potential trend. Maybe the way I chose to color the points is making this more difficult. There probably is no trend. It seems like there is no correlation between phenotype and ability to kill the the other species. It might be better to look at an individuals' fitness and its ability not to die, in order to determine if having a higher phenotype is beneficial.

@@

Starting parameters:

- sigma_i = 1, 
- recomb=1e-8, 
- sigma_in = 0.5,
- **sigma_M = 0.33**, 
- **K =1**, 
- SD = sigma_in,  
- SI = sigma_in,  
- surs = sigma_in, 
- SM = SI,  
- L = 4,  
- W = 35.0, 
- G = 1e8, 
- FECUN = 1/(L)),  
- RHO = FECUN/((1+FECUN) * K), 
- initializeRecombinationRate(recomb)

Interaction Constants:

- **interaction_rate = 0.05**,  
- PE = 0.1,  
- w = 10,  
- c = 0.0, 
- **some_value = 30 (half number of new individuals)**, 
- **sc_size = 10 (selection coefficient)**

@@

### Newts Get the Mutation

@@

Yes <- c(8, 9, 11, 3, 16)/50 * 100
No <- c(42, 41, 39, 47, 34)/50 * 100

@@

Seems like having more individuals and a higher selection coefficient lead to the mutation spreading to all of the individuals in the population. For most of the simulations the spreading out or dying out happens very quickly (under 1500 generations)

###Snakes Get the Mutation

@@

Yes <- c(7, 10, 4, 0, 19)/50 * 100
No <- c(43, 40, 46, 50, 31)/50 * 100
snake_results_df <- data.frame(Notes, Yes, No)
knitr::kable(snake_results_df, "simple")
```

This is also the case when snakes get the mutation. Although it was peculiar when the selection coefficient was very small there were no cases when the artificial mutation spread throughout the population.

###Both Newts and Snakes get the Mutation

@@

Snake_Yes <- 15/50 * 100
Newt_Yes <- 15/50 * 100
Snake_No <- 35/50 * 100
Newt_No <- 35/50 * 100

@@

When both species get the mutation I saw each combination happen sometimes the mutation would spread in both the snakes and newts populations. Other times only the mutation would only spread in one population and there were time when the mutation dies out in both populations.

Concluding notes:

The artificial mutation either stays in the population increasing rapidly or dies out in a few generations, suggesting that the mutation is spreading due to selection. The mutation does spread do to selection, but I think it can be quicker and I am not sure if it is due to the interaction between snakes and newts. I want to increase the rate of the interaction without creating areas where newts and snakes don't interact (holes). I also want to test the prediction that a higher phenotype might protect an individual from death. First, I will look at the correlation between phenotype and fitness (a measure of how likely an individual will survive) and see if they are positively or negatively correlated. However, there might be problems crease by spatial structure that might impact the correlation. So, the second thing I will do is crease and run a no space simulation to see the direct consequence the interaction had on individuals phenotypes. The only problem is determining how many newt and snakes will be interacting with each other?
